Fast and Error-Adaptive Count-Distinct Sketch \\for Influence Maximization

### 2021-01-21 paper.tex
Progress

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{subfiles}
\usepackage{url}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{subfig}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:~}}
\renewcommand{\algorithmicensure}{\textbf{Output:~}}
\newcommand\ovr[1]{\overrightarrow{#1}}
\newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
\usepackage{booktabs}
\usepackage{array}
\usepackage{color}
\usepackage{listings}
\usepackage{placeins}
\usepackage{enumitem}
%%%%%%
% add seconds to fig 7
% fix yaxis
% table 3-5 son satir 3-5
% fontlari buyult, relative score/time , fig 10 11
% notation
% Notes: 
% plot grouping/hue +
% table smallcaps +
% Time score memory center +
% Abstract
% Differences between infuser and us+
% time skecth diff between us +
% neden 0.005 +
% active vertex colors +

% GRID PARAM SEARCH
% Performance comparison vs others (why slowed down?)
% Error-Adaptive rebuilding sat
%%%%%
\ifCLASSOPTIONcompsoc
  \usepackage[nocompress]{cite}
\else
  \usepackage{cite}
\fi

@@

The study of efficient information/influence propagation in networks becomes an important area of research with several applications from many fields, such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.
As the study of these networks is imperative for educational, political, economic, and social purposes, a high-quality seed set to initiate the diffusion may have critical importance.
Furthermore, since the diffusion analysis may be time-critical, or increasing its coverage may be expensive in terms of computing resources and time, novel and efficient approaches to find good vertex sets that propagates the information/influence effectively is essential.

@@

Simulating a greedy algorithm in parallel is an obvious and straightforward workaround to reduce the execution time of IM kernels and make them scalable for large-scale networks. However, for large networks, a greedy approach with a good approximation guarantee does not come cheap even if a large number of processing units/cores are available on networks with billions of vertices and edges. Following similar attempts in the literature, we propose a parallel, sketch-based greedy approach that approximates the Monte-Carlo processes. The proposed approach does not exactly count the number of influenced vertices. Instead, it leverages Count-Distinct sketches. 
in this work, we apply parallelism in multiple levels; thread-level and instruction-level parallelism. While modern compilers employ instruction-level parallelism effectively and automatically for applications with regular memory access patterns, graph kernels are usually harder to deal with. The irregularity of the neighbor IDs. ..... due to their irregular memory access patterns, it is not a straightforward task for graph processing kernels.  Besides, vectorization attempts on such kernels typically fail to provide substantial speed-up in performance.

@@

% \item \acro can be around $200000\times$ faster compared to the traditional greedy approaches. It is usable on large graphs that have been considered as {\em too large} in the literature. For instance, the new algorithm runs in $2.09$, $0.08$, $0.36$ seconds on networks {\tt Amazon}, {\tt NetHEP}, {\tt NetPhy} with 16 threads where the sequential baseline takes $141.3$, $259.1$ and $1725.2$ seconds, respectively. In fact, with a 302,400 seconds~(3.5 days) timeout, the sequential baseline can process only the above-mentioned 3 (out of 12) real-life graphs, having 1.2M, 58.9K and 231.5K edges. On the other graphs, the original algorithm cannot complete the simulations within the time limit. However, \acro{} completes all of 12 graphs around 1200 seconds in total, where the maximum is 654 seconds for the {\tt Orkut} network having 3.1M vertices and 117.2M edges.

@@

\begin{table}[!ht]
    \caption{Table of notations}
    \label{tab:notation}
    \centering
    \begin{tabular}{|l|p{0.7\linewidth}|}
        \hline
        Variable & Definition  \\
        \hline
        $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
        $\Gamma_G(v)$   & Neighborhood of incoming edges to vertex $v$ in graph $G$\\ %%FIXME
        $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
        %$SCC(v) $       & Strongly connected component of vertex $v$\\
        $R_{G}(v)$      & Reachability set of vertex $v$ on graph $G$\\
%        $\overline{R_{G}(v)} & Complement of the vertex set $R_{G}(v)$\\
        \hline\hline
        $S$             & Seed set to maximize influence\\
        $K$             & Size of the seed set\\
        $\mathcal{R}$   & Number of Monte-Carlo simulations performed\\
        $\sigma_{G}(S)$ & Influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
        % $\sigma_{G}{(S,v)}$          & Marginal influence gain by adding vertex $v$ to seed set $S$\\
\hline\hline
        %$p$             & Sampling probability for edges\\
%        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
        $X_{r..n}$      & Slice of Vector X between r and r+n(not including)\\
        $h(u,v)$        & Hash function for edge $\{u,v\}$\\
        $h_{max}$       & Maximum value hash function $h$ can return\\
        %$X_r$           & Random number/hash generated for simulation $r$  \\
        \hline\hline
        $B$             & Batch size\\
        $e$             & Estimated reachability set size\\
        % $[a, \ldots, a]_B$      & Vector of size $B$, contains all $a$\\
        $M_u[j]$        & $j$th sketch register for vertex $u$\\
        $\varsigma $    & Influence gained before last sketch build\\
        $\sigma $       & Influence Score\\
        $\delta$        & Marginal Gain after last sketch build\\
        $\epsilon_{g}$    & Global estimation error threshold\\
        $\epsilon_{l}$    & Local estimation error threshold\\ 
        $\epsilon_{c$    & Non-convergenced vertex threshold\\
      %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
        \hline         
    \end{tabular}
\end{table}
\subsection{Influence Maximization}

@@

\begin{itemize}[leftmargin=*]
\item The {\bf Independent Cascade} process performs in iterations and activates the $v$ vertex if one of its (incoming) edges, $(u, v)$, is 
used during the iteration of diffusion, which has an expected probability of $w_{u, v}$, because $u$ was already influenced in the previous rounds. 
Activation probabilities are independent (from each other and previous activations) in the {\em independent} variant which we concentrate on in this paper, as in Figure~\ref{fig:ic}.
In theory, there can exist parallel and  independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via preprocessing.

@@

%Each edge $e=(s,v) \in E$ has a weight $w_{s,v}$. Each vertex $v$ has incoming edge list $Adj^{-1}(v)$ and $\sum_{s\in Adj^{-1}(v) }{w_{s,v}} \leq 1$. Also, each vertex $v$ has associated with a threshold $\theta_v$. Initially, $\theta$ is sampled uniformly, and seed set is set as activated. Then, until convergence is reached simulation ran to transfer $w_ij$ values from activated vertices to their neighborhoods, activating each vertex $v$ that reach $\theta_v$ value. Weights can be uniform i.e 0.1, 0.01, or 0.001 for all edges, as we observed in many work.

@@

The complexity analysis stays consistent for many diffusion models including {\em Independent Cascade}~(IC), {\em Linear Threshold}~(LT),  models. 
% Current studies focus on reducing the number of simulations run \cite{goyal2011celf++, goyal2011simpath}, sketch-based speedup methods\cite{SKIM}, and proxy methods that solve similar yet simpler problems \cite{kempe2003maximizing}. %FIXME too many methods, one french paper in python
%\cite{kempe2003maximizing} 
We concentrate on the independent cascade model in this paper, but the proposed methods are also relevant to the other models in the literature.
%  \[ \sigma(S^*)=\argmax_{S\subseteq V \land |S| \leq k } \sigma_{G}(S) \]

%is a simple diffusion model that Vertex v can be activated by any of incoming edges from activated vertices w with probability $p$. Given a seed set $S$ and influence probability $p$, the cascade model starts from the activated seed set and tries to diffuse until each of the out-going edges of active vertices are considered. The diffusion process considers all edges only once.

@@

For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for non-trivial graphs. 
If one-hot vectors are used to store reachability sets for constant insertion time, $O(n^2\mathcal{R})$ bits of memory is required and each merge operation has $O(n)$ time complexity. 
if Disjoints sets are used for storing reachability sets; $(n\bar{\sigma}\mathcal{R})$ memory is required to store all reachability sets, and each merge operation has $O(ackermann'(\sigma))$ complexity.

@@

Flajolet–Martin algorithm only stores how rare elements are in a multi-set.The rarity of the elements is often computed by counting leading zeros in the item's hash values.  The registers are initialized with zero values in beginning. Items are added by storing the longest leading zero count. Cardinality estimation can be done by taking 2 to the power of the stored value. Multiple registers and hash functions, $M[j]$ and $h_j$, are commonly used to reduce variance.
Adding item $x$ to sketch $M$, and its result $M'$ is shown in equation~\ref{eq:sketch-add}.

@@

\begin{figure*}[!ht]
    \begin{center}
    \includegraphics[width=\linewidth]{images/sketch-diffusion.pdf}
    \caption{(a) The initial state on the toy graph for \acro{}; all vertices have set as live(green) and their registers initialized with leading zero count of their hashes. (b) 
    % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
    For the live edge between Vertex 1 and 4, the register is set to the maximum of the respective register. Since the first register of vertex 1 is bigger, we only update the second register. Also, the edge between vertex 4 and 3 is only live in simulation 2, so we only set the maximum of those two registers to vertex 4's second register. Notice that, we are moving registers in reverse, from target to source of the edges. We set vertices 1 and 4 as live(green) since their registers have changed in this iteration (c) Vertex 1's register is updated and set as live again since vertex 4's registers are changed.  (d) All vertices have registers converged, there are no live vertices. }\label{fig:hf-processing} 
    \end{center}
    \end{figure*}
\subsection{Error-Adaptive Sketch Rebuilding}

@@

Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
The sketches are assumed as stale if the absolute error in the estimated total influence score is more than the global threshold, $\epsilon_{global}$, 
and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{local}$.

Before rebuilding stale sketches, the reachability set of latent seed set,$R_G(S')$, is marked as visited, 
and considered blocked in their respective simulations while rebuilding the sketches. Then, sketches are rebuild using Monte-Carlo simulations. After rebuilding, $mask$, which holds the cardinality estimate of the seed vertices added after the last rebuild, is cleared with all zeros.

@@

\begin{figure*}[!h]
    \begin{center}
        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_time.pdf}
        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_time.pdf}
        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_time.pdf}\\

        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_score.pdf}
        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_score.pdf}
        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_score.pdf}\\
    \end{center}
    \caption{Effect of $\epsilon$ parameters on \acro($J=256$, $\epsilon_c=0.02$) performance, using $\tau=18$ threads.}\label{fig:parameter-smallmultiples} 
\end{figure*}    
\begin{figure}[h] 
    \centering
    \includegraphics[width=1\linewidth]{images/converge-performance.pdf}
  \centering \caption{Geometic mean of \acro's performance and results quality on different $\epsilon_c$ parameters. ($J=256,\epsilon_l=0.3,\epsilon_g=0.01,\tau=18$) 
    \label{fig:conv-perf}} 
\end{figure}

@@

\begin{tabular}{l|rrrr|rrrr|rrrr}
\toprule
{} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
Method & {\sc HyperFuser} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc HyperFuser} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc HyperFuser} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
Dataset      &            &         &        &       &            &         &         &         &            &       &      &      \\
\midrule
{\tt Amazon}       &       1.30 &  124.38 &   5.58 & 63.73 &       96.9 &  1.041x &  1.000x &  0.562x &       0.17 & 21.62 & 0.90 & 6.78 \\
{\tt DBLP}         &       1.61 &  177.99 &   5.71 & 28.24 &      106.6 &  1.068x &  1.027x &  1.036x &       0.27 & 31.24 & 0.95 & 3.12 \\
{\tt Epinions}     &       1.11 &   12.16 &   0.50 &  8.29 &      635.3 &  1.026x &  1.001x &  0.939x &       0.06 &  0.78 & 0.07 & 1.04 \\
{\tt LiveJournal}  &      13.25 & 4172.69 & 118.82 & 19.35 &    37174.1 &  1.010x &  0.995x &  0.957x &       3.97 & 27.43 & 2.78 & 2.00 \\
{\tt NetHEP}       &       0.31 &    2.22 &   0.31 &  1.96 &       80.2 &  1.065x &  0.993x &  0.871x &       0.01 &  0.80 & 0.04 & 0.33 \\
{\tt NetPhy}       &       0.39 &    7.40 &   0.40 &  1.00 &      124.5 &  1.042x &  0.999x &  0.777x &       0.03 &  2.01 & 0.08 & 0.16 \\
{\tt Orkut}        &      30.22 &       - & 780.22 & 41.82 &   158842.6 &       - &  0.997x &  1.001x &       5.19 &     - & 7.81 & 1.77 \\
{\tt Pokec}        &      11.05 &  149.34 &   5.04 & 18.40 &     1095.1 &  1.032x &  1.027x &  0.925x &       1.57 & 10.16 & 1.40 & 1.74 \\
{\tt Slashdot0811} &       1.18 &    6.93 &   0.40 &  1.00 &      576.4 &  1.015x &  0.983x &  0.942x &       0.06 &  0.76 & 0.09 & 0.13 \\
{\tt Slashdot0902} &       1.14 &    6.96 &   0.40 &  1.17 &      610.5 &  1.022x &  0.998x &  0.953x &       0.06 &  0.71 & 0.08 & 0.14 \\
{\tt Twitter}      &       1.10 &  171.17 &   5.40 &  1.60 &     3458.7 &  1.006x &  0.990x &  0.942x &       0.09 &  2.02 & 0.12 & 0.15 \\
{\tt Youtube}      &       1.95 &   46.61 &   2.42 & 13.24 &     1820.8 &  1.025x &  1.013x &  1.000x &       0.73 &  3.96 & 0.48 & 1.39 \\
\bottomrule
Geo. Mean wrt.&1.00x&28.19x&1.69x&3.46x&1.00x&1.03x&1.00x&0.90x&1.00x&22.75x&1.65x&3.58x \\ \acro
\end{tabular}

@@

Dataset      &            &         &         &        &            &         &         &         &            &       &       &      \\
\midrule
{\tt Amazon }       &       0.96 &  107.94 &    3.28 &  59.32 &      152.7 &  1.037x &  1.024x &  0.390x &       0.17 & 18.11 &  0.55 & 6.40 \\
{\tt DBLP }         &       0.73 &   73.37 &    2.85 &  18.71 &      233.5 &  1.043x &  1.005x &  0.997x &       0.27 & 11.92 &  0.52 & 2.05 \\
{\tt Epinions }     &       0.82 &  112.08 &    3.78 &   5.07 &     2480.1 &  1.006x &  0.983x &  0.984x &       0.06 &  1.95 &  0.10 & 0.68 \\
{\tt LiveJournal }  &      16.72 &       - &  386.37 &  16.23 &   155375.8 &       - &  0.996x &  0.993x &       3.97 &     - &  6.64 & 1.45 \\
{\tt NetHEP }       &       0.26 &    1.84 &    0.23 &   1.89 &      129.1 &  1.036x &  0.997x &  0.826x &       0.01 &  0.60 &  0.03 & 0.31 \\
{\tt NetPhy }       &       0.24 &    3.33 &    0.23 &   0.86 &      320.5 &  1.010x &  0.985x &  0.732x &       0.03 &  0.67 &  0.05 & 0.12 \\
{\tt Orkut }        &      42.37 &       - & 1870.35 & 114.82 &   650157.1 &       - &  1.000x &  1.000x &       5.19 &     - & 20.13 & 3.43 \\
{\tt Pokec }        &      11.65 & 4148.03 &   88.89 &   7.25 &    44685.8 &  1.004x &  0.996x &  0.988x &       1.57 & 39.98 &  2.09 & 0.78 \\
{\tt Slashdot0811 } &       0.84 &  102.96 &    3.70 &   0.87 &     2882.1 &  1.003x &  0.984x &  0.976x &       0.06 &  2.01 &  0.10 & 0.08 \\
{\tt Slashdot0902 } &       0.90 &  129.31 &    4.19 &   0.88 &     3061.5 &  1.008x &  0.992x &  0.980x &       0.06 &  2.42 &  0.11 & 0.08 \\
{\tt Twitter }      &       0.90 &  390.36 &   10.96 &   1.22 &     9628.6 &  1.004x &  0.992x &  0.978x &       0.09 &  4.91 &  0.23 & 0.09 \\
{\tt Youtube }      &       2.18 &  534.41 &   14.86 &  16.97 &     9042.7 &  1.009x &  0.994x &  1.006x &       0.73 &  7.10 &  0.48 & 1.73 \\
\bottomrule
Geo. Mean wrt.&1.00x&100.14x&5.45x&3.58x&1.00x&1.02x&1.00x&0.88x&1.00x&36.26x&1.91x&2.82x \\ \acro
\end{tabular}

@@

Independent Path Algorithm~(IPA)~\cite{IPA} by Kim~et~al runs a proxy model and prunes paths with probabilities less than a given threshold. IPA uses {\tt OpenMP} to work on independent paths in parallel. The approach only keeps a dense but small part of the network and scalable on only sparse networks. Liu~et~al. proposed IMGPU~\cite{IMGPU}, an IM  estimation method by utilizing a bottom-up traversal algorithm. It performs a single Monte-Carlo simulation on many GPU threads to find the reachability of the seed set. It is $5.1\times$ faster than {\sc MixGreedy} on a CPU. The GPU implementation is up to $60\times$ faster with an average speedup of  $24.8\times$.

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{subfiles}
\usepackage{url}
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{subfig}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:~}}
\renewcommand{\algorithmicensure}{\textbf{Output:~}}
\newcommand\ovr[1]{\overrightarrow{#1}}
\newcommand\myeq{\mkern1.5mu{=}\mkern1.5mu}
\usepackage{booktabs}
\usepackage{array}
\usepackage{color}
\usepackage{listings}
\usepackage{placeins}
\usepackage{enumitem}
%%%%%%
% notation 
%%%%%
\ifCLASSOPTIONcompsoc
  \usepackage[nocompress]{cite}
\else
  \usepackage{cite}
\fi

@@

The study of efficient information/influence propagation in networks becomes an important area of research with several applications from many fields, such as viral marketing~\cite{leskovec2007dynamics, trusov2009effects}, social media analysis~\cite{zeng2010social, moreno2004dynamics}, and recommendation systems~\cite{lu2012recommender}.
As the study of these networks is imperative for educational, political, economic, and social purposes, a high-quality seed set to initiate the diffusion may have critical importance.
Furthermore, since the diffusion analysis may be time-critical, or increasing its coverage may be expensive in terms of computing resources and time, novel and efficient approaches to find good vertex sets that propagate the information/influence effectively are essential.

@@

Simulating a greedy algorithm in parallel is a straightforward workaround to reduce the execution time of IM kernels and make them scalable for large-scale networks. However, for large networks, a greedy approach with a good approximation guarantee does not come cheap even if a large number of processing units/cores are available on networks with billions of vertices and edges. Following similar attempts in the literature, we propose a parallel, sketch-based greedy approach that approximates the Monte-Carlo processes. The proposed approach does not exactly count the number of influenced vertices. Instead, it leverages Count-Distinct sketches.

@@

@@

\begin{table}[!ht]
    \caption{Table of notations}
    \label{tab:notation}
    \centering
    \begin{tabular}{|l|p{0.7\linewidth}|}
        \hline
        Variable & Definition  \\
        \hline
        $G = (V,E)$     & Graph $G$ with vertices $V$ and edges $E$ \\
        $\Gamma_G(v)$   & Neighborhood of incoming edges to vertex $v$ in graph $G$\\ %%FIXME
        $w_{u,v}$       & Probability of $u$ directly influencing $v$ \\
        %$SCC(v) $       & Strongly connected component of vertex $v$\\
        $R_{G}(v)$      & Reachability set of vertex $v$ on graph $G$\\
%        $\overline{R_{G}(v)} & Complement of the vertex set $R_{G}(v)$\\
        \hline\hline
        $S$             & Seed set to maximize influence\\
        $K$             & Size of the seed set\\
        $\mathcal{R}$   & Number of Monte-Carlo simulations performed\\
        $\sigma_{G}(S)$ & Influence score of $S$ in $G$, i.e., expected number of vertices reached from $S$ in $G$\\
        % $\sigma_{G}{(S,v)}$          & Marginal influence gain by adding vertex $v$ to seed set $S$\\
\hline\hline
        %$p$             & Sampling probability for edges\\
%        $P(s,v)_r $     & Random probability generated for selecting edge vertices $s$ to $v$ in simulation $r$\\
        $X_{r..n}$      & Slice of Vector X between r and r+n(not including)\\
        $h(u,v)$        & Hash function for edge $\{u,v\}$\\
        $h_{max}$       & Maximum value hash function $h$ can return\\
        %$X_r$           & Random number/hash generated for simulation $r$  \\
        \hline\hline
        $B$             & Batch size\\
        $e$             & Estimated reachability set size\\
        % $[a, \ldots, a]_B$      & Vector of size $B$, contains all $a$\\
        $M_u[j]$        & $j$th sketch register for vertex $u$\\
        $\varsigma $    & Influence gained before last sketch build\\
        $\sigma $       & Influence Score\\
        $\delta$        & Marginal Gain after last sketch build\\
        $\epsilon_{g}$    & Global estimation error threshold\\
        $\epsilon_{l}$    & Local estimation error threshold\\ 
        $\epsilon_{c}$    & Non-convergenced vertex threshold\\
      %  $x[[i, j]]$   & Slice of vector  $x$ between indices $i$ and $j$, not including $j$ \\ 
        \hline         
    \end{tabular}
\end{table}
\subsection{Influence Maximization}

@@

\begin{itemize}[leftmargin=*]
\item The {\bf Independent Cascade} process performs in iterations and activates the $v$ vertex if one of its (incoming) edges, $(u, v)$, is 
used during the iteration of diffusion, which has an expected probability of $w_{u, v}$, because $u$ was already influenced in the previous rounds. 
Activation probabilities are independent (from each other and previous activations) in the {\em independent} variant which we concentrate on in this paper, as in Figure~\ref{fig:ic}.
In theory, there can exist parallel and  independent $\{u, v\}$ edges in $E$. In practice, they are merged to a single $\{u,v\}$ edge via pre-processing.

@@

@@

The complexity analysis stays consistent for many diffusion models including {\em Independent Cascade}~(IC), {\em Linear Threshold}~(LT),  models. We concentrate on the independent cascade model in this paper, but the proposed methods are also relevant to the other models in the literature.

@@

For directed graphs, storing reachability sets for all vertices and merging these sets are infeasible for non-trivial graphs. 
If one-hot vectors are used to store reachability sets for constant insertion time, $O(n^2\mathcal{R})$ bits of memory is required and each merge operation has $O(n)$ time complexity. 
if Disjoints sets are used for storing reachability sets; $(n\bar{\sigma}\mathcal{R})$ memory is required to store all reachability sets, and each merge operation has $O(Ackermann'(\sigma))$ complexity.

@@

Flajolet–Martin algorithm only stores how rare elements are in a multi-set.The rarity of the elements is often computed by counting leading zeros in the item's hash values.  The registers are initialized with zero values in the beginning. Items are added by storing the longest leading zero count. Cardinality estimation can be done by taking 2 to the power of the stored value. Multiple registers and hash functions, $M[j]$ and $h_j$, are commonly used to reduce variance.
Adding item $x$ to sketch $M$, and its result $M'$ is shown in equation~\ref{eq:sketch-add}.

@@

\begin{figure*}[!ht]
    \begin{center}
    \includegraphics[width=\linewidth]{images/sketch-diffusion.pdf}
    \caption{(a) The initial state on the toy graph for \acro{}; all vertices have set as live(green) and their registers initialized with leading zero count of their hashes. (b) 
    % For all live edges,$e_{ij}$, respective registers are merged and set to source vertex $j$'s register, $M_j \leftarrow Max(M_i, M_j)$. 
    For the live edge between Vertex 1 and 4, the register set to the maximum of the respective register. Since the first register of vertex 1 has a larger value, we only update the second register. Also, the edge between vertex 4 and 3 is only live in simulation 2, so we only set the maximum of those two registers to vertex 4's second register. Notice that we are moving registers in reverse, from target to source of the edges. We set vertices 1 and 4 as live(green) since their registers have changed in this iteration (c) Vertex 1's register is updated and set as live again since vertex 4's registers are changed.  (d) All vertices have registers converged, there are no live vertices. }\label{fig:hf-processing} 
    \end{center}
    \end{figure*}
\subsection{Error-Adaptive Sketch Rebuilding}

@@

Since building sketches with \acro is very fast, we exploit this by rebuilding sketches after observing large cardinality estimation errors.
After adding vertices to the seed set, \acro performs Monte-Carlo simulations to estimate the reachability of the latent seed set.
The sketches are assumed as stale if the absolute error in the estimated total influence score is more than the global threshold, $\epsilon_{g}$, 
and the marginal gain estimation error after the last sketch is larger than a local threshold $\epsilon_{l}$.

Before rebuilding stale sketches, the reachability set of latent seed set, $R_G(S')$, is marked as visited, 
and considered blocked in their respective simulations while rebuilding the sketches. Then, sketches are rebuild using Monte-Carlo simulations. After rebuilding, $mask$, which holds the cardinality estimate of the seed vertices added after the last rebuild, is cleared with all zeros.

@@

\begin{figure*}[!h]
    \begin{center}
        \subfloat[LiveJournal execution time in seconds\label{fig:lj-time}]{%
        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_time.pdf}
    }
    \subfloat[Orkut execution time in seconds\label{fig:orkut-time}]{%
        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_time.pdf}
        }
    \subfloat[Pokec execution time in seconds\label{fig:pokec-time}]{%
        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_time.pdf}
        }\\
        \subfloat[LiveJournal Influence Score\label{fig:lj-score}]{%
        \includegraphics[width=0.33\linewidth]{images/heatmap_LiveJournal_score.pdf}
        }
    \subfloat[Orkut Influence Score\label{fig:lj-score}]{%
        \includegraphics[width=0.33\linewidth]{images/heatmap_Orkut_score.pdf}
        }
    \subfloat[Pokec Influence Score\label{fig:pokec-score}]{%
        \includegraphics[width=0.33\linewidth]{images/heatmap_Pokec_score.pdf}
        }\\
    \end{center}
    \caption{Effect of $\epsilon$ parameters on \acro($J=256$, $\epsilon_c=0.02$) performance, using $\tau=18$ threads.}\label{fig:parameter-smallmultiples} 
\end{figure*}    
\begin{figure}[h] 
    \centering
    \includegraphics[width=1\linewidth]{images/converge-performance.pdf}
  \centering \caption{Geometic mean of \acro's performance and results quality on different $\epsilon_c$ parameters. ($J=256,\epsilon_l=0.3,\epsilon_g=0.01,\tau=18$) 
    \label{fig:conv-perf}} 
\end{figure}

@@

\begin{tabular}{l|rrrr|rrrr|rrrr}
\toprule
{} & \multicolumn{4}{c|}{Time} & \multicolumn{4}{c|}{Score} & \multicolumn{4}{c}{Memory} \\
Method & {\sc HyperFuser} &    {\sc Tim+} &    {\sc Imm} &  {\sc Skim} & {\sc HyperFuser} &    {\sc Tim+} &     {\sc Imm} &    {\sc Skim} & {\sc HyperFuser} &  {\sc Tim+} &  {\sc Imm} & {\sc Skim} \\
Dataset      &            &         &        &       &            &         &         &         &            &       &      &      \\
\midrule
{\tt Amazon}       &       1.30 &  124.38 &   5.58 & 63.73 &       96.9 &  1.041x &  1.000x &  0.562x &       0.17 & 21.62 & 0.90 & 6.78 \\
{\tt DBLP}         &       1.61 &  177.99 &   5.71 & 28.24 &      106.6 &  1.068x &  1.027x &  1.036x &       0.27 & 31.24 & 0.95 & 3.12 \\
{\tt Epinions}     &       1.11 &   12.16 &   0.50 &  8.29 &      635.3 &  1.026x &  1.001x &  0.939x &       0.06 &  0.78 & 0.07 & 1.04 \\
{\tt LiveJournal}  &      13.25 & 4172.69 & 118.82 & 19.35 &    37174.1 &  1.010x &  0.995x &  0.957x &       3.97 & 27.43 & 2.78 & 2.00 \\
{\tt NetHEP}       &       0.31 &    2.22 &   0.31 &  1.96 &       80.2 &  1.065x &  0.993x &  0.871x &       0.01 &  0.80 & 0.04 & 0.33 \\
{\tt NetPhy}       &       0.39 &    7.40 &   0.40 &  1.00 &      124.5 &  1.042x &  0.999x &  0.777x &       0.03 &  2.01 & 0.08 & 0.16 \\
{\tt Orkut}        &      30.22 &       - & 780.22 & 41.82 &   158842.6 &       - &  0.997x &  1.001x &       5.19 &     - & 7.81 & 1.77 \\
{\tt Pokec}        &      11.05 &  149.34 &   5.04 & 18.40 &     1095.1 &  1.032x &  1.027x &  0.925x &       1.57 & 10.16 & 1.40 & 1.74 \\
{\tt Slashdot0811} &       1.18 &    6.93 &   0.40 &  1.00 &      576.4 &  1.015x &  0.983x &  0.942x &       0.06 &  0.76 & 0.09 & 0.13 \\
{\tt Slashdot0902} &       1.14 &    6.96 &   0.40 &  1.17 &      610.5 &  1.022x &  0.998x &  0.953x &       0.06 &  0.71 & 0.08 & 0.14 \\
{\tt Twitter}      &       1.10 &  171.17 &   5.40 &  1.60 &     3458.7 &  1.006x &  0.990x &  0.942x &       0.09 &  2.02 & 0.12 & 0.15 \\
{\tt Youtube}      &       1.95 &   46.61 &   2.42 & 13.24 &     1820.8 &  1.025x &  1.013x &  1.000x &       0.73 &  3.96 & 0.48 & 1.39 \\
\bottomrule
Geo. Mean wrt.&1.000x&28.191x&1.687x&3.465x&1.000x&1.032x&1.002x&0.899x&1.000x&22.750x&1.650x&3.581x \\ \acro
\end{tabular}

@@

Dataset      &            &         &         &        &            &         &         &         &            &       &       &      \\
\midrule
{\tt Amazon }       &       0.96 &  107.94 &    3.28 &  59.32 &      152.7 &  1.037x &  1.024x &  0.390x &       0.17 & 18.11 &  0.55 & 6.40 \\
{\tt DBLP }         &       0.73 &   73.37 &    2.85 &  18.71 &      233.5 &  1.043x &  1.005x &  0.997x &       0.27 & 11.92 &  0.52 & 2.05 \\
{\tt Epinions }     &       0.82 &  112.08 &    3.78 &   5.07 &     2480.1 &  1.006x &  0.983x &  0.984x &       0.06 &  1.95 &  0.10 & 0.68 \\
{\tt LiveJournal }  &      16.72 &       - &  386.37 &  16.23 &   155375.8 &       - &  0.996x &  0.993x &       3.97 &     - &  6.64 & 1.45 \\
{\tt NetHEP }       &       0.26 &    1.84 &    0.23 &   1.89 &      129.1 &  1.036x &  0.997x &  0.826x &       0.01 &  0.60 &  0.03 & 0.31 \\
{\tt NetPhy }       &       0.24 &    3.33 &    0.23 &   0.86 &      320.5 &  1.010x &  0.985x &  0.732x &       0.03 &  0.67 &  0.05 & 0.12 \\
{\tt Orkut }        &      42.37 &       - & 1870.35 & 114.82 &   650157.1 &       - &  1.000x &  1.000x &       5.19 &     - & 20.13 & 3.43 \\
{\tt Pokec }        &      11.65 & 4148.03 &   88.89 &   7.25 &    44685.8 &  1.004x &  0.996x &  0.988x &       1.57 & 39.98 &  2.09 & 0.78 \\
{\tt Slashdot0811 } &       0.84 &  102.96 &    3.70 &   0.87 &     2882.1 &  1.003x &  0.984x &  0.976x &       0.06 &  2.01 &  0.10 & 0.08 \\
{\tt Slashdot0902 } &       0.90 &  129.31 &    4.19 &   0.88 &     3061.5 &  1.008x &  0.992x &  0.980x &       0.06 &  2.42 &  0.11 & 0.08 \\
{\tt Twitter }      &       0.90 &  390.36 &   10.96 &   1.22 &     9628.6 &  1.004x &  0.992x &  0.978x &       0.09 &  4.91 &  0.23 & 0.09 \\
{\tt Youtube }      &       2.18 &  534.41 &   14.86 &  16.97 &     9042.7 &  1.009x &  0.994x &  1.006x &       0.73 &  7.10 &  0.48 & 1.73 \\
\bottomrule
Geo. Mean wrt.&1.000x&100.140x&5.448x&3.582x&1.000x&1.016x&0.996x&0.879x&1.000x&36.264x&1.909x&2.820x \\ \acro
\end{tabular}

@@

Independent Path Algorithm~(IPA)~\cite{IPA} by Kim~et~al runs a proxy model and prunes paths with probabilities less than a given threshold. IPA uses {\tt OpenMP} to work on independent paths in parallel. The approach only keeps a dense but small part of the network and scalable on only sparse networks. Liu~et~al. proposed IMGPU~\cite{IMGPU}, an IM  estimation method by utilizing a bottom-up traversal algorithm. It performs a single Monte-Carlo simulation on many GPU threads to find the reachability of the seed set. It is $5.1\times$ faster than {\sc MixGreedy} on a CPU. The GPU implementation is up to $60\times$ faster with an average speed-up of  $24.8\times$.
